Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-31 bounds-files/sec03-approx-kde.tex
Minor fixes + Dong's address update
Fix minor typo.

Note that this version is far simpler than other dual-tree algorithms that have
been proposed for approximate kernel density estimation \citep[see, for
instance][]{gray2003nonparametric}; however, this version is sufficient for our
runtime analysis.  Real-world implementations, such as the one found in
\textbf{mlpack} \citep{mlpack2013}, tend to be far more complex.

@@

\begin{thm}
Assume that $\mathcal{K}(\cdot, \cdot)$ is a kernel satisfying the assumptions
of the previous subsection.  Then, given a query set $S_q$ of size $O(N)$ and a
reference set $S_r$ of size $O(N)$ with expansion constant $c_r$, and using the
approximate kernel density estimation \texttt{BaseCase()} and \texttt{Score()}
as given in Algorithms \ref{alg:kde_base_case} and \ref{alg:kde_score},
respectively, with the traversal given in Algorithm \ref{alg:cover-tree-dual},
the running time of approximate kernel density estimation for some error
parameter $\epsilon$ is bounded by
%\begin{equation}
$O(c_r^{8 + \lceil \log_2 \zeta \rceil} (N + I_t(\mathscr{T}_q) + \theta))$
%\end{equation}
with $\zeta = -\mathcal{K}'(h) \mathcal{K}^{-1}(\epsilon) \epsilon^{-1}$,
$I_t(\mathscr{T}_q)$ defined as in Definition \ref{def:imbalance}, and $\theta$
defined as in Lemma \ref{lem:extcase3}.

>>>>

Note that this version is far simpler than other dual-tree algorithms that have
been proposed for approximate kernel density estimation \citep[see, for
instance,][]{gray2003nonparametric}; however, this version is sufficient for our
runtime analysis.  Real-world implementations, such as the one found in
\textbf{mlpack} \citep{mlpack2013}, tend to be far more complex.

@@

\begin{thm}
Assume that $\mathcal{K}(\cdot, \cdot)$ is a kernel with bandwidth $h$ satisfying the assumptions
of the previous subsection.  Then, given a query set $S_q$ of size $O(N)$ and a
reference set $S_r$ of size $O(N)$ with expansion constant $c_r$, and using the
approximate kernel density estimation \texttt{BaseCase()} and \texttt{Score()}
as given in Algorithms \ref{alg:kde_base_case} and \ref{alg:kde_score},
respectively, with the traversal given in Algorithm \ref{alg:cover-tree-dual},
the running time of approximate kernel density estimation for some error
parameter $\epsilon$ is bounded by
%\begin{equation}
$O(c_r^{8 + \lceil \log_2 \zeta \rceil} (N + I_t(\mathscr{T}_q) + \theta))$
%\end{equation}
with $\zeta = -\mathcal{K}'(h) \mathcal{K}^{-1}(\epsilon) \epsilon^{-1}$,
$I_t(\mathscr{T}_q)$ defined as in Definition \ref{def:imbalance}, and $\theta$
defined as in Lemma \ref{lem:extcase3}.
